Timeliness of security updates for Android

### 2014-08-27 securityupdates.tex
Talk about the vulnerabilities timeline

>>>>

\begin{figure}
 \centering
 \includegraphics[width=\columnwidth]{figures/vulnerabilities_timeline}
 \caption{Timeline of vulnerabilities}
 \label{fig:vulnerabilities_timeline}
\end{figure}

The dates of discovery of vulnerabilities in the \texttt{androidvulnerabilities.org} is not uniform.
Figure~\ref{fig:vulnerabilities_timeline} shows the dates of discovery and, when later, the dates when a version of Android which fixed the vulnerability was shipped.
Some vulnerabilities (RageAgainstTheCage adb, levitator, zergRush abd TwerkMyMoto) were fixed in released versions of Android before they were discovered and so are shown as vertical lines while others were known for months before a version of Android which fixed them was shipped.
During the period in which Device Analyzer data was collected the date when a version of Android with the fix was observed on a Device Analyzer device is taken as the date that version was released, before that the release date as best as we can determine is used.
There is no canonical source of Android release dates, our best guesses and supporting references are available from \texttt{androidvulnerabilities.org}.
